Modeling Interventions

### 2021-03-04 paper/paper.Rmd
minor edits, last refs
we're now at 3463 words and 33 refs (goal: 3000 and 30)

keywords          : "early language learning; language acquisition; vocabulary development"
wordcount         : "3334"

@@

**Leveraged learning and the role of processing**. As the model results above show, older children accumulate language from their input faster than younger children. 
Why? One potential reason is that independent developmental or maturational factors simply make older children better at remembering their experiences. 
Another possibility -- not mutually exclusive -– is that children *leverage* their knowledge of language to learn faster [@mitchell2009]. 
This leverage idea is consistent with many proposed mechanisms for language learning. For example, if children reason about new vocabulary items by exclusion [@markman1988], they could get better at learning new words just by having more potential items to exclude from consideration. 
Yet a third possibility –- again not mutually exclusive with the others -– is that children are getting better at using the words they know. 
Several recent studies have found that a surprising proportion of variance in the rate of young children’s vocabulary growth is accounted for by the speed with which individual children are able to process familiar words [e.g., @fernald2006picking; @marchman2016early].
Disentangling these distinct explanations will require careful measurement of both vocabulary and the potential mechanisms of leverage [cf. @lewis2020].

**Beyond vocabulary**. The "standard model" that we have proposed is a model of the accumulation of words, but language is rich, complex system in which words are inflected morphologically and composed syntactically to express compositional meanings. In early conceptions of language learning, syntax and morphology were thought of as distinct and unconnected, but this conception has not been borne out empirically. Instead, evidence from large-scale data show again and again that the language system is "tightly woven," with extremely tight correlations between the acquisition of words, morphology, and syntax [@frank2021]. Theoretically, accumulator models like the standard model are generic models of skill acquisition. Given the perspective that language learning is a form of skill acquisition [@chater2018language], such connections could lead the way towards exensions of the standard model to the accumulation of broader units of language like constructions.

@@

# References
```{r create_r-references}
#r_refs(file = "references.bib")
```

>>>>

keywords          : "early language learning; language acquisition; vocabulary development"
wordcount         : "3463"

@@

**Leveraged learning and the role of processing**. As the model results above show, older children accumulate language from their input faster than younger children. 
Why? One potential reason is that independent developmental or maturational factors simply make older children better at remembering their experiences. 
Another possibility -- not mutually exclusive -– is that children *leverage* their knowledge of language to learn faster [@mitchell2009]. 
This leverage idea is consistent with many proposed mechanisms for language learning. For example, if children reason about new vocabulary items by exclusion [@markman1988children], they could get better at learning new words just by having more potential items to exclude from consideration. 
Yet a third possibility –- again not mutually exclusive with the others -– is that children are getting better at using the words they know. 
Several recent studies have found that a surprising proportion of variance in the rate of young children’s vocabulary growth is accounted for by the speed with which individual children are able to process familiar words [e.g., @fernald2006picking; @marchman2016early].
Disentangling these distinct explanations will require careful measurement of both vocabulary and the potential mechanisms of leverage [cf. @lewis2020role].

**Beyond vocabulary**. The "standard model" that we have proposed is a model of the accumulation of words, but language is rich, complex system in which words are inflected morphologically and composed syntactically to express compositional meanings. 
In early conceptions of language learning, syntax and morphology were thought of as distinct and unconnected, but this conception has not been borne out empirically. 
Instead, evidence from large-scale data show again and again that the language system is "tightly woven," with extremely tight correlations between the acquisition of words, morphology, and syntax [@wordbankbook]. 
Theoretically, accumulator models like the standard model are generic models of skill acquisition. 
Given the perspective that language learning is a form of skill acquisition [@chater2018language], such connections could lead the way towards extensions of the standard model to the accumulation of broader units of language like constructions.

@@

# References
```{r create_r-references}
#r_refs(file = "references.bib") # 31 refs right now
```
